Online Classification of arXiv Papers Based on Your Preferences

### 2014-05-16 Paper.tex

Finally, it would be worthwhile to explore other online learning algorithms and possible other features that might improve predictive performance. Considering a wider variety of text classification models would probably produce better results, and the limited time to develop this tool compromised our ability to develop and play around with some of these models. Nevertheless that is a huge body of work in and of itself.

>>>>

Finally, it would be worthwhile to explore other online learning algorithms and possibly other features that might improve predictive performance. Considering a wider variety of text classification models would probably produce better results, and the limited time to develop this tool compromised our ability to develop and play around with some of these models. Nevertheless that is a huge body of work in and of itself.
\end{document}

\section{Conclusion}
We have developed a tool to present users with potentially interesting articles from the massive number of papers available on Arxiv.  Online learning methods are used to learn the user's preferences over time, but in order for them to be useful, they cannot present the user with every single prediction.  Instead, we weaken the algorithms to present the user with all articles it predicts will be interesting, and only some of those it feels will not be interesting.  We show that in this context, a bound on the expected number of mistakes can still be achieved under the some assumptions.  Finally, we test several algorithms on labeled data, and show that they perform comparably to the original learning algorithms, but require less input from the user.\\
